Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2025-01-15 paper.qmd
Updated Figure 16

<!--add langevitour screenshots and youtube animation link-->
```{r}
#| label: fig-mnist-tri-proj
#| fig-pos: H
#| fig-height: 10
#| fig-width: 10
#| out-width: 60%
#| fig-cap: "Model in \\gD{}, on the layout a and three views of the fit in projections from $10\\text{-}D$, for the MNIST digit 1 data ($n =  7877$ and $p = 10$). There is a big non-linear cluster and a small clusterlocated very close to one corner of the big cluster. There is a twisted pattern that is hardly visible in the static plot. Video of the langevitour animation are available at <need to add the link>."

free(trimesh_removed_mnist) + mnist_proj_tsne_model1 +
  mnist_proj_tsne_model2 + mnist_proj_tsne_model3 +
  plot_layout(ncol = 2)

>>>>

<!--add langevitour screenshots and youtube animation link-->
```{r}
#| label: fig-mnist-tri-proj
#| fig-pos: H
#| fig-height: 30
#| fig-width: 10
#| out-width: 100%
#| fig-cap: "Model in \\gD{}, on the layout a and three views of the fit in projections from $10\\text{-}D$, for the MNIST digit 1 data ($n =  7877$ and $p = 10$). There is a big non-linear cluster and a small clusterlocated very close to one corner of the big cluster. There is a twisted pattern that is hardly visible in the static plot. Video of the langevitour animation are available at <need to add the link>."

free(trimesh_removed_mnist) + mnist_proj_tsne_model1 +
  mnist_proj_tsne_model2 + #mnist_proj_tsne_model3 +
  plot_layout(ncol = 3)
